Software Citation Principles

### 2016-04-17 sc-principles/software-citation-principles.tex
adding MIcah Altman to participant list in Appendix

Notable examples around metadata include DOAP~\cite{DOAP}, an early metadata
term set used by the Open Source Community, as well as more recent community
efforts like the AAS workshop~\cite{aas-software-index}, Project
CRediT~\cite{casrai-credit}, Ontosoft~\cite{ontosoft}, CodeMeta~\cite{codemeta},
or the terms and classes defined at \href{https://schema.org}{www.schema.org} related to the
\href{https://schema.org/SoftwareApplication}{\texttt{SoftwareApplication}} class.

@@

>>>>

Content specifications for software metadata vary across communities, and include 
include DOAP~\cite{DOAP}, an early metadata
term set used by the Open Source Community, as well as more recent community
efforts like the AAS workshop~\cite{aas-software-index}, Project
CRediT~\cite{casrai-credit}, Ontosoft~\cite{ontosoft}, 
or the terms and classes defined at \href{https://schema.org}{www.schema.org} related to the
\href{https://schema.org/SoftwareApplication}{\texttt{SoftwareApplication}} class.   In addition, 
language-specific software metadata schemes are in widespread use, including the Debian 
package format~\cite{Debian_policy}, Python package descriptions~\cite{pypi}, and R package descriptions~\cite{wickham_r_2015}, but these are typically
conceived for software build, packaging,and distribution rather than citation.  CodeMeta~\cite{codemeta} 
has created a crosswalk among these software metadata schemes and an exchange format that 
allows software repositories to effectively interoperate.

@@

Micah Altman, MIT
